Predicting sales of newly published books

### 2015-08-14 paper.tex
creando la sección de estado del arte

% Cuando se edita un nuevo libro, es importante determinar el número de ejemplares que se van a imprimir en papel en cada edición, ya que a la editorial puede suponerle un alto coste imprimir volúmenes que finalmente no se vendan.
% Así pues, se hace necesario disponer de herramientas automáticas, basadas en algoritmos de extracción de la información que ofrezcan estimaciones de la cantidad de copias de cierto libro que se pueden llegar a vender.
% En ese sentido, en colaboración con la empresa PRM Consultores S.C.A. se ha llevado a cabo el análisis de un conjunto de datos que describen la tirada editorial en los últimos años. Como parte del estudio, se han aplicado diversos métodos de clasificación y predicción para determinar cuántos libros se pueden llegar a vender.
% Muchas empresas ven la estimación de las ventas de un nuevo producto como uno de las tareas más complicadas de llevar a cabo, ya que en muchos casos no suele haber datos históricos que sirvan de guía.
%% Many companies must face, as one of the most difficult tasks to
%% accomplish, new product sales estimation, since in many cases no
%% historical data to serve as guide is available. 
%% Moreover, some of them lack the knowledge about forecasting methods
%% and they can only make decisions based on the expert sales
  %% managers. 
% Eliminado esto.
When a new book is published the publishing house faces the problem of
how many books should be printed. Printing too many is the main issue,
since it implies a loss of investment. That is why it is an issue to
print the right amount of book, and do so even before the book has
reached shelves. That is the problem we try to solve in this paper.
% Es más, realizar predicciones poco precisas puede dar lugar a decisiones erróneas que resulten en un exceso de producción que no se llegue a vender o incluso a una producción deficitaria.
%Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
% Es el caso del problema de la tirada editorial, en el que las empresas editoriales deben estimar el número de volúmenes a imprimir, siempre cuidando de no imprimir más de los que realmente acaben vendiéndose. Así pues, un sistema automático de predicción de ventas de libros para estimar la tirada editorial sería de gran ayuda para las empresas editoriales.
%That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling. Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
% En la bibliografía se proponen diferentes métodos de predicción de
% ventas, principalmente para la industria de la moda. En esos
% trabajos, cuando las ventas son estables, con una tendencia clara a
% lo largo del tiempo, los métodos clásicos son una buena opción. Sin
% embargo, en el caso de nuevos productos, tales como la publicación
% para su venta de un nuevo libro, los métodos clásicos no funcionan
% bien. 
% In the literature, different methods of sales prediction, mainly for
% the fashion industry are proposed. 
% Esto no pega nada en el abstract - JJ
%In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
%However, in the case of new products, such as a new book publishing, classical methods do not work properly.
% En este trabajo se propone el uso de un método basado en reglas de decisión para abordar el problema de la predicción de la tirada editorial. Dicho método ha sido validado por la empresa que cedió los datos ya que ofrece información sobre el proceso de decisión y no necesita de intervención humana, ni para el funcionamiento ni para la interpretación.
%In this paper, a rule-based decision method is proposed to address the
%problem of predicting the publishing roll.  
% It's not proposed. It just obtained the best result with WEKA. - JJ 
% Publishing roll? ¿Qué es? - JJ
In this paper, which works with data on published books in Spain, we
first apply a data visualization and preprocessing strategy to find
out what are the relevant variables in the prediction of sales, and
then use standard data mining software to predict sales, and from them
deduce print roll, based on those variables. Our work discovers which
are the most relevant variables when predicting sales, and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishing houses,
since the obtained models provide information on the decision process and
does not require human intervention either for the operation or for
interpretation.
\end{abstract}

 %El abstract no me gusta nada. Debería ir a la introducción. Hay que
 %enmarcar el problema (hace falta predecir las ventas para no imprimir
 %más de la cuenta) hacer un resumen de lo hecho y decir el
 %resultado. Lo más importante es, ¿cuál es el selling point?

%********************************************************************************
\section{Introduction and State of the Art}

% A partir de datos históricos de tiradas editoriales se plantea el uso de varios modelos basados en redes neuronales artificiales para la clasificación y predicción de la tirada de nuevos títulos editoriales.

% En principio, los datos de que se dispone para entrenar los modelos son: autor del libro, materia, precio, editorial, ventas netas y tirada.

% Como primer objetivo se define el conjunto de datos y se estudian las entradas actuales para los modelos de predicción y las que se podrían obtener para mejorar las predicciones.

% Se espera obtener modelos basados en redes neuronales capaces de realizar predicciones de la tirada global.

% A una empresa, lanzar un nuevo producto le supone un alto riesgo debido a la complejidad de los procesos de producción y distribución. En este ámbito, disponer de estimaciones de futuras ventas del nuevo producto resulta extremadamente importante \cite{ChingChin2010}.
A company that intends to release a new product has a high risk due to
the complexity of the production and distribution processes. A newly
launched product is also new to the company, and sales forecasts can
only be based on the experience of similar products. 
In this scope, having accurate estimates of future sales of the new
product is extremely important \cite{ChingChin2010} so that production
runs do not exceed predicted sales.

% La industria editorial se basa en varios pasos y procesos productivos / La publicación de un libro requiere de varios pasos / Además, la distribución es importante y juega un papel importante
In this sense, the publishing industry is based on very particular and
established production process, and publishing a book requires several
steps, between which the distribution is important and plays an
important role. 
% Esos pasos hacen que el proceso y las decisiones individuales en cada paso sean muy importantes. Una de esas decisiones es el número de ejemplares a imprimir.
The publishing process and individual decisions at each step are very
important. One of those decisions is the number of copies to print. % ¿Esto que tiene que ver con la frase anterior? - JJ

% Así pues, un sistema de predicción debe tener en cuenta muchos detalles acerca del funcionamiento del proceso editorial.
Thus, a suitable prediction system for new books should take into
account many details about how the editorial process works. % y? - JJ

% La implementación de un buen sistema de predicción requiere, no sólo de un buen estudio del estado del arte en este campo, sino también de un conocimiento preciso de las operaciones y retos de la industria editorial y su cadena de producción.
Implementing a good forecasting tool requires not only a good study of
the state of the art in this field, but also an accurate knowledge of
the operations and challenges facing the publishing industry and its
supply chain. % ¿eso es lo que vamos a hacer? - JJ

% En el ámbito de la industria de la moda se trata de un problema muy
% complejo, sujeto a ciertos requisitos \cite{SThomassey2014} y que se
% ha abordado con diversos métodos en las últimas décadas
% \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}. 
% Pero ¿a santo de qué viene aquí la industria de la moda? Habrá que
% introducirlo diciendo... El problema de la industria similar es
% parecido a otras industrias, etc, etc...

In the field of fashion predicting sales is very complex problem, subject
to certain requirements \cite{SThomassey2014} and has been faced using
various methods in recent decades
\cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.  % Este
                                % párrafo no dice absolutamente nada
                                % ni aporta nada. Si se menciona la
                                % industria de la moda, es que vamos a
                                % aprender algo de ella. ¿Cuáles son
                                % los requisitos? ¿Cuáles son los
                                % métodos? ¿Vamos a aprender de ellos?
                                % - JJ

% Interesa imprimir un número de ejemplares suficiente pero sin pasarse, ya que los no vendidos suponen pérdidas, mientras que si se imprimieron de menos, siempre se pueden imprimir más.
In the field of publishing industry, it is more important printing an
adequate number of copies but not too much, as the unsold volumes will
lead to losses, whereas if the number of printed copies was not
enough, you can always print more. Thus, it is extremely important to
forecast the sales a new book might achieve. % Hala, otro salto. ¿Qué
                                % tiene que ver esto con el párrafo
                                % anterior? - JJ

% El uso de una herramienta de predicción es útil si se usa adecuadamente, y para ello conviene conocer el producto, las características de las ventas y la forma de distribuirlo, ya que son detalles que afectan al proceso \cite{Armstrong2001,SThomassey2014}.
Thus, using a predictive tool is very useful when used properly; in
this sense, it is very important to know the product, the
characteristics of sales and how to distribute it, as those details
affect the process \cite{Armstrong2001,SThomassey2014}. % ¿Esto
                                % también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ

% En la industria editorial influyen diversos factores que hacen que las ventas fluctúen. Estos factores no suelen ser controlables y en ocasiones no son conocidos. Algunos tienen que ver con las decisiones sobre compras, otros con el tráfico de mercancías o con la estrategia de distribución \cite{Little1998}.
Book sales are influenced by various factors that make
them fluctuate.  These factors are usually not controllable and
sometimes unknown. 
Some have to do with decisions on purchases, others with freight
traffic, and others with the distribution strategy
\cite{Little1998}. % ¿Qué hacen todas estas cosas? ¿Vamos a tenerlas
                   % en cuenta?

% El impacto que tienen es difícil de estimar y no es constante en el tiempo, de ahí la dificultad de identificarlos adecuadamente y medir su influencia \cite{DeToni2000}. Además, algunas pueden presentar correlaciones entre ellas. Sin embargo, dichas correlaciones pueden detectarse utilizando métodos de análisis de datos, como el SOM (y otros de R) \textbf{ESPECIFICAR CUÁLES}
Their impact is difficult to estimate and it is not constant over time, hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.

% Generalmente las editoriales usan datos históricos y es un experto el que aplica su conocimiento y usa diversas variables externas para obtener predicciones bastante adecuadas.  El proceso habitual de predicción de ventas se basa en el uso de algún tipo de software que genera una predicción que sirve como base u orientación, pero que finalmente refina un experto, ya que la empresa requiere un modelo interpretable y entendible.  Por ejemplo, el experto puede subir o bajar la predicción de las ventas en función de algún periodo de ofertas.  Sin embargo, los análisis son imprecisos y pueden no tener todas las variables en cuenta.  Además, el proceso suele ser tedioso para un conjunto considerable de datos, e incluso, diferentes expertos pueden llegar a diferentes predicciones a partir de los mismos datos.
Publishers generally use historical data and an expert analyzes that
data and applies his knowledge using external variables to obtain quite
appropriate predictions. % ¿cita para esto?  - JJ
However, in recent years the sales are forecasted using an
application. % ¿Cita para esto? - JJ
This is used as the foundation over which an expert applies his
knowledge, as the company might require an interpretable and
understandable model. For example, the expert might increase or
decrease the sales prediction based on season or sales period.
However, the obtained analysis can be imprecise and may not take all
the variables into account. 
In addition, the process is often tedious, especially when the amount
of data is large, and even, different experts can reach different
predictions from the same data set. % We NEED a reference for this!!!
                                % - JJ
% Es por estas razones que la industria requiere que se adapten mejores técnicas de predicción a sus necesidades para realizar estimaciones de las ventas.
For these reasons, the industry requires the best suited forecasting
techniques to be adopted so that, estimating sales task is carried out
properly.

% El uso de herramientas de predicción puede ser beneficioso para una empresa editorial para optimizar la producción y así mejorar sus ganancias o minimizar pérdidas \cite{Zhao2001}. Un ejemplo es la optimización de las ventas \cite{Mattila2002}, mejorando el margen de ganancia al vender toda la tirada editorial.
Using predictive tools can benefit a publishing company to optimize production and improve their profits or minimize losses \cite{Zhao2001}. 
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole publishing roll.

\bigskip
%---------- estado del arte
% ¿Su propia sección? En ese caso, todo lo del estado del arte de
% arriba debería eliminarse - JJ

% En la bibliografía se pueden encontrar diversas propuestas para llevar a cabo la predicción de ventas en diferentes áreas. Por un lado, ciertos métodos cualitativos se basan en la experiencia de expertos, mientras que los métodos basados en el análisis de series temporales utilizan información histórica para hacer las predicciones \cite{ChingChin2010,FaderHardie2005,Madsen2008}.
In the literature several proposals to perform the prediction of sales
in different areas can be found.  %frase que no dice nada. ¿Por qué no
                                %empiezas enmarcando el estado del
                                %arte? Methods to predict book sales
                                %have been generally based on ... - JJ
On the one hand, several qualitative methods are based on an expert
experience, while time series prediction methods are based on using
historical data to make predictions
\cite{ChingChin2010,FaderHardie2005,Madsen2008}. % Hasta ahora no has
                                % dicho cuál es el problema. Tienes
                                % que decir claramente qué tienes y
                                % qué quieres. - JJ

%El uso de métodos de predicción de series temporales es quizás la técnica más usada para la predicción de ventas. Entre las técnicas más conocidas destacan las técnicas estadísticas \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. 
Using time series prediction methods is perhaps the most used
technique to tackle the sales forecasting task. 
In this sense, among the most popular techniques include statistical techniques \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. 
% Sin embargo, la eficiencia de estas técnicas depende en gran medida del campo de aplicación y de los datos que conforman el problema. Concretamente, aquellas técnicas que requieren de una gran cantidad de datos no son las más apropiadas para realizar la predicción de ventas de nuevos productos \cite{ChingChin2010}.
However, the efficiency of these techniques depends largely on the field of application and the problem data. 
Specifically, techniques that require a large amount of data for predicting sales of new products are not the most suitable for this task \cite{ChingChin2010}.

% En cualquier caso, en diversos trabajos ha quedado demostrado que una reducción de los errores de predicción en las ventas da como resultado una mejora en la cadena de producción \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
Anyway, several studies have demonstrated that improving sale predictions (a reduction of forecasting errors) results in an improvement in the production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

% Por otro lado, diferentes autores han propuesto métricas para determinar la bondad de las estimaciones. Sin embargo, las más comunmente utilizadas por las empresas son las basadas en el análisis de los errores cometidos (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.
On the other hand, different authors have proposed metrics to determine the accuracy of estimates. 
However, most companies use metrics based on the analysis of errors (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.

% Finalmente, existen casos en los que las predicciones se ven influenciadas por variables externas que hay que tener en cuenta, como la estacionalidad, promociones o modas \cite{Lapide1999}. Algunos autores proponen reducir las variaciones en los datos causadas por esas variables para mejorar la precisión de las predicciones \cite{Sheikh2003,Schrieber2005}. % p.ej. separar los datos relativos a una estación de otras para clasificar por separado.
Finally, in many cases the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions \cite{Lapide1999,ChernWSF15}.
In this sense, some authors propose reducing variations in the data caused by such variables to improve the accuracy of predictions
 \cite{Sheikh2003,Schrieber2005}.

% Por el tipo de problema que queremos abordar en este artículo, los métodos clásicos de predicción no son útiles, por lo que deberemos analizarlos previamente con otras herramientas. Además, puesto que las editoriales necesitan modelos que expliquen las predicciones ofrecidas, ciertos métodos tipo caja negra pueden no resultar adecuados a igualdad de precisión en las predicciones.
Taking into account the kind of problem we address in this paper, the classical forecasting methods are not useful. 
Thus, we must analyze raw data using other tools, prior to apply forecasting techniques.
In addition, since publishers need models to explain obtained predictions, black box forecasting methods may not be suitable for this problem.

\bigskip
%---------- final de la intro

The rest of this paper is structured as follows:
%Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography to BLA BLA BLA.
Section \ref{sec:problem} describes the new book publishing problem, followed by Section \ref{sec:methodology} where the experimental setup and the methodology considered in the study is presented. 
Section \ref{sec:experiments} reports and analyzes the obtained results with a real data set.
Finally, conclusions and future work are presented in Section \ref{sec:conclusionsAndFutureWork}.

>>>>

%% Many companies must face, as one of the most difficult tasks to
%% accomplish, new product sales estimation, since in many cases no
%% historical data to serve as guide is available. 
%% Moreover, some of them lack the knowledge about forecasting methods
%% and they can only make decisions based on the expert sales
  %% managers. 
% Eliminado esto.
When a new book is published the publishing house faces the problem of
how many books should be printed. Printing too many is the main issue,
since it implies a loss of investment. That is why it is an issue to
print the right amount of book, and do so even before the book has
reached shelves. That is the problem we try to solve in this paper.
%Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
%That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling. Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
% In the literature, different methods of sales prediction, mainly for
% the fashion industry are proposed. 
% Esto no pega nada en el abstract - JJ
%In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
%However, in the case of new products, such as a new book publishing, classical methods do not work properly.
%In this paper, a rule-based decision method is proposed to address the
%problem of predicting the publishing roll.  
% It's not proposed. It just obtained the best result with WEKA. - JJ 
% Publishing roll? ¿Qué es? - JJ
In this paper, which works with data on published books in Spain, we
first apply a data visualization and preprocessing strategy to find
out what are the relevant variables in the prediction of sales, and
then use standard data mining software to predict sales, and from them
deduce print roll, based on those variables. Our work discovers which
are the most relevant variables when predicting sales, and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishing houses,
since the obtained models provide information on the decision process and
does not require human intervention either for the operation or for
interpretation.
\end{abstract}

%********************************************************************************
\section{Introduction}

% A partir de datos históricos de tiradas editoriales se plantea el uso de varios modelos para la clasificación y predicción de la tirada de nuevos títulos editoriales.

A company that intends to release a new product has a high risk due to
the complexity of the production and distribution processes. A newly
launched product is also new to the company, and sales forecasts can
only be based on the experience of similar products. 
In this scope, having accurate estimates of future sales of the new
product is extremely important \cite{ChingChin2010} so that production
runs do not exceed predicted sales.

In this sense, the publishing industry is based on very particular and
established production process, and publishing a book requires several
steps, between which the distribution is important and plays an
important role. 
The publishing process and individual decisions at each step are very
important. 
% One of those decisions is the number of copies to print. 
  % ¿Esto que tiene que ver con la frase anterior? - JJ
Thus, a suitable prediction system for new books should take into
account many details about how the editorial process works. % y? - JJ

Implementing a good forecasting tool requires not only a good study of
the state of the art in this field, but also an accurate knowledge of
the operations and challenges facing the publishing industry and its
supply chain. % ¿eso es lo que vamos a hacer? - JJ

% introducirlo diciendo... El problema de la industria similar es
% parecido a otras industrias, etc, etc...
In the field of fashion predicting sales is very complex problem, subject
to certain requirements \cite{SThomassey2014} and has been faced using
various methods in recent decades
\cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.  % Este
                                % párrafo no dice absolutamente nada
                                % ni aporta nada. Si se menciona la
                                % industria de la moda, es que vamos a
                                % aprender algo de ella. ¿Cuáles son
                                % los requisitos? ¿Cuáles son los
                                % métodos? ¿Vamos a aprender de ellos?
                                % - JJ

In the field of publishing industry, it is more important printing an
adequate number of copies but not too much, as the unsold volumes will
lead to losses, whereas if the number of printed copies was not
enough, you can always print more. Thus, it is extremely important to
forecast the sales a new book might achieve. % Hala, otro salto. ¿Qué
                                % tiene que ver esto con el párrafo
                                % anterior? - JJ

Thus, using a predictive tool is very useful when used properly; in
this sense, it is very important to know the product, the
characteristics of sales and how to distribute it, as those details
affect the process \cite{Armstrong2001,SThomassey2014}. % ¿Esto
                                % también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ

Book sales are influenced by various factors that make
them fluctuate.  These factors are usually not controllable and
sometimes unknown. 
Some have to do with decisions on purchases, others with freight
traffic, and others with the distribution strategy \cite{Little1998}. 
  % ¿Qué hacen todas estas cosas? ¿Vamos a tenerlas en cuenta?

Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}.

Publishers generally use historical data and an expert analyzes that
data and applies his knowledge using external variables to obtain quite
appropriate predictions. % ¿cita para esto?  - JJ
However, in recent years the sales are forecasted using an
application. % ¿Cita para esto? - JJ
This is used as the foundation over which an expert applies his
knowledge, as the company might require an interpretable and
understandable model. For example, the expert might increase or
decrease the sales prediction based on season or sales period.
However, the obtained analysis can be imprecise and may not take all
the variables into account. 
In addition, the process is often tedious, especially when the amount
of data is large, and even, different experts can reach different
predictions from the same data set. % We NEED a reference for this!!! - JJ

For these reasons, the industry requires the best suited forecasting
techniques to be adopted so that, estimating sales task is carried out
properly.

Using predictive tools can benefit a publishing company to optimize 
production and improve their profits or minimize losses \cite{Zhao2001}. 
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole publishing roll.

The rest of this paper is structured as follows:
Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to the prediction of sales.
Then, Section \ref{sec:problem} describes the new book publishing problem, followed by Section \ref{sec:methodology} where the experimental setup and the methodology considered in the study is presented. 
Section \ref{sec:experiments} reports and analyzes the obtained results with a real data set.
Finally, conclusions and future work are presented in Section \ref{sec:conclusionsAndFutureWork}.

%********************************************************************************
\section{State of the art}
\label{sec:soa}

In the literature several proposals to perform the prediction of sales
in different areas can be found.  %frase que no dice nada. ¿Por qué no
                                %empiezas enmarcando el estado del
                                %arte? Methods to predict book sales
                                %have been generally based on ... - JJ
On the one hand, several qualitative methods are based on an expert
experience, while time series prediction methods are based on using
historical data to make predictions
\cite{ChingChin2010,FaderHardie2005,Madsen2008}. % Hasta ahora no has
                                % dicho cuál es el problema. Tienes
                                % que decir claramente qué tienes y
                                % qué quieres. - JJ

Using time series prediction methods is perhaps the most used
technique to tackle the sales forecasting task. 
In this sense, among the most popular techniques include 
statistical techniques \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. 
However, the efficiency of these techniques depends largely on the field of application and the problem data. 
Specifically, techniques that require a large amount of data for predicting sales of new products are not the most suitable for this task \cite{ChingChin2010}.

Anyway, several studies have demonstrated that improving sale predictions (a reduction of forecasting errors) results in an improvement in the production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

On the other hand, different authors have proposed metrics to determine the accuracy of estimates. 
However, most companies use metrics based on the analysis of errors (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.

Finally, in many cases the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions \cite{Lapide1999,ChernWSF15}.
In this sense, some authors propose reducing variations in the data caused by such variables to improve the accuracy of predictions
 \cite{Sheikh2003,Schrieber2005}.

Taking into account the kind of problem we address in this paper, the classical forecasting methods are not useful. 
Thus, we must analyze raw data using other tools, prior to apply forecasting techniques.
In addition, since publishers need models to explain obtained predictions, black box forecasting methods may not be suitable for this problem.
